Multiple testing with logical dependencies

### 2013-08-08 paper/draft.tex
Added section with one-sided hypotheses

\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
%% Comments
%\newcommand{\fcomment}[1]{ } % Turn off
\newcommand{\fcomment}[1]{\footnote{{\color{red} #1}}} % Turn on
\newcommand{\ie}{{\em i.e.,}~}
\newcommand{\cf}[1]{\mathbf{1}_{\left\{#1\right\}}}

@@

>>>>

\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
%% Comments
%\newcommand{\fcomment}[1]{ } % Turn off
\newcommand{\fcomment}[1]{\footnote{{\color{red} #1}}} % Turn on
\newcommand{\ie}{{\em i.e.,}~}
\newcommand{\indf}[1]{\mathbf{1}_{\left\{#1\right\}}}
%\newcommand{\text}[1]{\textrm{#1}}
\newcommand{\R}{\mathbb{R}}

@@

From conditions \ref{} it can be easily seen that while problems of
one sided hypotheses may be treated by matroids, already for simple
problems the correspondence between flats and strictly exhaustive sets
is not one to one. Nevertheless an alternative approach to this class
of problems can be found in the theory of oriented matroids.

First let us define a one sided multiple testing problem

\begin{definition}
  Let $\bs{X}$ denote an $m$ dimensional random vector with
  distribution function $P_{\bs{\mu}}$ from some parametric family
  $\mathscr{P} = \{P_{\bs{\theta}}: \bs{\theta} \in \mathbb{R}^m\}$. A
  family of {\em one sided linear contrast hypotheses} is defined by a
  contrast matrix $\bs{A} \in \mathbb{R}^{m\times n}$ and vector
  $\bs{b} \in \mathbb{R}^n$ that define a the family of null
  hypotheses of the form $\mathscr{H} = \{H_i: \bs{A_i}^t\bs{\mu} \leq
  b_i,i \in \{1,...,n\}\}$, where $\bs{A}_i$ denotes the $i$-th column
  of $\bs{A}$ and $b_i$ the $i$-th componenth of $\bs{b}$.
\end{definition}

Now observe that each hypothesis $H_i$ corresponds to a hyperplane
$h_i = \{\bs{x} \in \mathbb{R}^m: \bs{A}_i^t\bs{x} = b_i\}$ that divides
$\mathbb{R}^m$ into two regions $h_i^+ = \{\bs{x} \in \mathbb{R}^m:
\bs{A}_i^t\bs{x} < b_i\}$ and $h_i^- = \{\bs{x} \in \mathbb{R}^m: \bs{A}_i^t\bs{x} >
b_i\}$ giving rise to a sign function:
\begin{equation}
  \label{eq:sign}
  \delta_i(\bs{x}) = \left\{
\begin{array}{ll}
  + & \text{if } \bs{x} \in h_i^+\\
  0 & \text{if } \bs{x} \in h_i \\
  - & \text{if } \bs{x} \in h_i^-\\
\end{array}\right.
\end{equation}

Further for every $\bs{x} \in \mathbb{R}^m$ we have  sign vector
$\bs{\delta}{\bs{x}}= (\delta_1(\bs{x}),...,\delta_n(\bs{x}))$. Now
for each $i$ and some parameter value $\bs{\theta} \in \bs{\Theta} = \R^m$,
$\delta_i(\bs{\theta})$ tells us whether the corresponding value is under the null
hypotheses on its border, or under the alternative. Accordingly,
$\bs{\delta}(\bs{\theta})$ tells us in which combination of true and
false null hypotheses $H_i$ correspond to $\bs{\theta}$. Let
\begin{equation}
\label{eq:faces}
\mathcal{F}(\bs{A},\bs{b} = \{\bs{\delta}(\bs{x}): \bs{x} \in \R^m\}
\end{equation}

and for some $F \in \mathcal{F}$ define
\begin{equation}
  \label{eq:partition}
  \Theta_F = \{\bs{x} \in \R^m: \bs{\delta}(\bs{x}) = F\}
\end{equation}

then we have $\bigcup_{F \in \mathcal{F}} \Theta_F = \bs{\Theta} =
\R^m$ and for any $\Theta_F \cap \Theta_G = \emptyset$ for any $F \neq
G$. Consequently, $\{\Theta_F:F \in \mathcal{F}$ represents a
partition of the parameter space and each element in $\mathcal{F}$
uniquely identifies some {\em non-empty} element of that partition. Consequently,
following the Partitioning Principle \cite[]{finner2002partitioning}
if we have level $\alpha$ tests $\varphi_F(X)$ for each $F \in
\mathcal{F}$ a test that rejects $H_i$ for observed values $X$ if
$\varphi_F(X) = 1$ for all $F$ with $F_i \geq 1$ controls the FWER in
the strong sense. For example one may use  weighted Bonferroni tests
\begin{equation}
  \label{eq:bonferroni}
  \varphi_F = \indf{\min_{i:F_i \geq 0}p_i \leq w_{F,i}}
\end{equation}
where the $w_{F,i}$ are can be computed using a graphical approach.

Note that as $\Theta_F$, $F \in \mathcal{F}$ the $\mathscr{L} = \{I \subset \{1,...,m\}: \exists F \in
\mathcal{F}: F_i \geq 0 \forall i \in I\}$ are all strictly exhaustive sets.

The question remains how to compute $\mathcal{F}$. For this observe
that the $h_i$ define a hyperplane configuration and $\mathcal{F}$ is
just the face lattice of the corresponding oriented
matroid. Consequently, $\mathcal{F}$ can be found using algorithms
for arrangement construction from polyhedral programming
\cite{Avis-KF-92,Avis-KF-96,Ferrez-KF-Liebling-01} which are
polynomial in time and input size and compact in space!

\begin{definition}
  Consider a family of hypotheses $\mathscr{H} =$
\end{definition}
